### 2021-01-13 paper/natastron/2nd_draft/methods.tex
minor fixes

Finally, we also consider bias in asteroseismic detections. The probability of an asteroseismic detection with \kepler scales with temperature and radius (i.e. scales inversely with \logg, and therefore main sequence age) \cite{m_chaplin+2011, m_schofield+2019}. More active, magnetic stars may also suppress their oscillation modes, making it more likely to detect seismic oscillations in older stars \cite{m_mathur+2019}. Through these two effects, asteroseismology is biased towards detecting older over younger stars. As it is older stars, undergoing magnetic braking, that are required to drive the distinction between stellar models, we do not expect this observing bias to effect our conclusions.

>>>>

Finally, we also consider bias in asteroseismic detections. The probability of an asteroseismic detection with \kepler scales with temperature and radius (i.e. scales inversely with \logg, and therefore main sequence age), \rtwo{and detections are unlikely below roughly $5200\, K$} \cite{m_chaplin+2011, m_schofield+2019}. \rtwo{Very young ($\lesssim 2\, \rm{Gyr}$), very magnetically active stars may also suppress their oscillation modes. \cite{m_mathur+2019}. Though these two effects impose a bias on asteroseismic populations, they do so outside the parameter range on which our comparison takes place. As it is older stars, undergoing magnetic braking, that are required to drive the distinction between stellar models, we conclude that our seismic sample can be assumed to be complete for the purposes of this work.}
